The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-05 paper.tex
update

  \begin{equation}
     |\mathbf{B}(R, z)|=B_{0}\exp{-z/z_{0}}\exp{-R/R_{0}},
  \end{equation}

@@

\section{Results}
\label{Results}
  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp.png}
    \caption{
             The pressure (top), temperature (middle), and number density (bottom) slices\
             through a bipolar jet sources injecting along $z=-y$ direction from\
             the origin for a duration of 1.2 Myr under four different cases from left to right.\
             Comparison between the cases with a clumpy (first column from left)\
             and with a smooth disc (second) in a stratified atmosphere\
             shows that the initial density distribution of the dense disc has an insignificant effect\
             on the overall dynamics of bubbles. However, the outer bubbles with the smooth disc\
             in an uniform atmosphere (third) is spherical-shape,\
             suggesting the stratification facilitates the outer bubbles elongation significantly.\
             Also, the first three and the rightmost columns show that the most inner bubbles (dashed box)\
             can only appear associated with the disc, and without the disc, the outer bubbles will be tilted,
             indicating the dense disc is crucial for\
             the axis-symmetrical outer bubbles and of the most inner bubbles formation.
             }
    \label{fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp}
  \end{figure}

\subsection{X-ray}
The X-ray emissivity in an energy range 1.4–1.6 keV is calculated\
using the MEKAL model \citep{Xray-1,Xray-2,Xray-3}\
implemented in the utility XSPEC \citep{XSPEC}, assuming solar metallicity.\

@@

\subsection{Microwave haze}

  \begin{subequations}
     \begin{align}
        &\frac{dE}{dtd\nu dV} =\nonumber\\
        &\frac{4\pi\mathbb{C}e^{3}B^{0.5(p+1)}}{m_{\text{e}}c^{2}}\
        \left(\frac{3e}{4\pi m_{\text{e}}c}\right)^{0.5(p-1)}\
        a(p)\nu^{-0.5(p-1)}.\\
        &a(p)=\nonumber\\
             &\frac{2^{0.5(p-1)}\sqrt{3}\Gamma\left[\left(3p-1\right)/12\right]\
                                        \Gamma\left[\left(3p+9\right)/12\right]\
                                        \Gamma\left[\left(p+5\right)/4\right]}
        {8\sqrt{\pi}(p+1)\Gamma\left[\left(p+7\right)/4\right]}
     \end{align}
  \end{subequations}

\subsection{Gamma-ray}

@@

where $\sigma_{T}$ is the Thomson cross section, $c$ speed of light, $m_{\text{e}}$ electron mass,\
$n(\epsilon)$ the photon number density of ISRF per energy, $\gamma$ the Lorentz factor of CRe,\
$\mathbb{C}$ and $p$ are the normalization constant and spectral index of CRe power-law spectrum,\
$\gamma_{\text{min}}(\epsilon)$ is the minimum required Lorentz factor of CRe such that CRe is energetic sufficient for\
producing scattered photon at the energy $\epsilon_{1}$ from an incident photon energy $\epsilon$.\
$\gamma_{\text{max}}$ is the maximum CRe Lorentz factor in the spectrum, i.e. $\gamma_{\text{max}}=10^{6}$.

@@

\begin{figure*}
  \includegraphics[width=\linewidth]{figures/fig__GammaRay_100e9_1e6_angle_000.png}
  \caption{The observed (left) and simulated (right) photon flux\
           in the energy bin $76.8-153.6$ GeV.\
           Note that the left panel is the\
           photon flux of the diffuse component reconstructed by the D$^3$PO\
           algorithm \citep{Selig2015} that analyzes\
           the photon data from the \textit{Fermi} Large Area Telescope \citep{Atwood2009}\
           and removes the contribution from point-like component.
           The red arrow at the center of the right\
           panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
           to the disc normal in 1.2 Myr.
  }
  \label{fig__gammaRay}
\end{figure*}

\begin{figure*}
  \includegraphics[width=\linewidth]{figures/fig__spectrum.png}
  \caption{
      Simulated microwave spectra (colored lines in left) averaged over $20^{\circ}<|b|<30^{\circ}$, $|l|<10^{\circ}$.\
      The data point represents the \textit{WMAP} data in the 23 GHz K band and\
      the shaded bow-tie area indicates the range\
      of synchrotron spectral indices allowed for the \textit{WMAP} haze \citep{Dobler_2008}.\
      Simulated gamma-ray spectra (colored lines in right column)\
      of the \textit{Fermi} bubbles calculated for a longitude range of\
      $|l|<10^{\circ}$ for different latitude bins.\
      The gray band represents the observational data of \citet{Ackermann2014}.\
      The rows from top to bottom show the microwave (left) and gamma-ray (right) spectra\
      with CRe spectra index $2.2, 2.4$ and $2.6$.\
      The CRe cutoff energy is $1.1\times10^{6}m_{\text{e}}c^{2}$ in all cases.
      %At larger $p$, the microwave spectrum was found to be steeper as $I_{\nu}\propto \nu^{-(p-1)/2}$.
  }
  \label{fig__gammaRay}
\end{figure*}

@@

Since the jets encounter a larger column depth of cloudsalong their path,\
they interact more strongly with the dense ISM.\
The jets do not immediately clear a channel along the inclined axis of launch.\
Rather, the dense clouds deflect the jets, which then decelerate\
and launch a sub-relativistic outflow along the minor axis following the path of least resistance.

>>>>

  \begin{equation}
     |\mathbf{B}(R, z)|=B_{0}\exp{-z/z_{0}}\exp{-R/R_{0}},
     \label{magnetic-field}
  \end{equation}

@@

\section{Results}

 \Cref{fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp} shows\
 the pressure (top), temperature (middile), number density (bottom) of slices on $x=0$ plane\
 passing through a bipolar jet sources injecting along $z=-y$ direction from\
 the origin for a duration of 1.2 Myr under four different cases from left to right.\
 Comparison between the cases with a clumpy (first column from left)\
 and with a smooth disc (second) in a stratified atmosphere\
 shows that the initial density distribution of the dense disc has an insignificant effect\
 on the overall dynamics of bubbles. However, the outer bubbles with the smooth disc\
 in an uniform atmosphere (third) is spherical-shape,\
 suggesting the stratification facilitates the outer bubbles elongation significantly.\
 Also, the first three and the rightmost columns show that the most inner bubbles (dashed box)\
 can only appear associated with the disc, and without the disc, the outer bubbles will be tilted,
 indicating the dense disc is crucial for\
 the axis-symmetrical outer bubbles and of the most inner bubbles formation.

\label{Results}
  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp.png}
    \caption{
             The pressure (top), temperature (middle), and number density (bottom) slices\
             passing through a bipolar jet sources injecting along $z=-y$ direction from\
             the origin for a duration of 1.2 Myr under four different cases from left to right.\
             Comparison between the cases with a clumpy (first column from left)\
             and with a smooth disc (second) in a stratified atmosphere\
             shows that the initial density distribution of the dense disc has an insignificant effect\
             on the overall dynamics of bubbles. However, the outer bubbles with the smooth disc\
             in an uniform atmosphere (third) is spherical-shape,\
             suggesting the stratification facilitates the outer bubbles elongation significantly.\
             Also, the first three and the rightmost columns show that the most inner bubbles (dashed box)\
             can only appear associated with the disc, and without the disc, the outer bubbles will be tilted,
             indicating the dense disc is crucial for\
             the axis-symmetrical outer bubbles and of the most inner bubbles formation.
             }
    \label{fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp}
  \end{figure}

  \subsection{X-ray}
  The X-ray emissivity in an energy range 0.6 --- 1.0 keV is calculated\
  using the MEKAL model \citep{Xray-1,Xray-2,Xray-3}\
  implemented in the utility XSPEC \citep{XSPEC}, assuming solar metallicity.\

@@

\subsection{Gamma-ray and microwave emission}
  In this section, we compare the simulated gamma-ray and microwave\
  spectra based on the leptonic AGN jet model with the\
  observed spectra of the Fermi bubbles and the microwave haze.

@@

where $\sigma_{T}$ is the Thomson cross section, $c$ speed of light,\
$n(\epsilon)$ the photon number density of ISRF per energy, $\gamma$ the Lorentz factor of CRe,\
$\mathbb{C}$ and $p$ are the normalization constant and spectral index of CRe power-law spectrum.
$\gamma_{\text{min}}(\epsilon)$ is the minimum required Lorentz factor of CRe such that CRe is energetic sufficient for\
producing scattered photon at the energy $\epsilon_{1}$ from an incident photon energy $\epsilon$.\
$\gamma_{\text{max}}$ is the maximum CRe Lorentz factor in the spectrum, i.e. $\gamma_{\text{max}}=10^{6}$.

@@

\begin{figure*}
  \includegraphics[width=\linewidth]{figures/fig__GammaRay_100e9_1e6_angle_000.png}
  \caption{The observed (left) and simulated (right) photon flux\
           in the energy bin $76.8-153.6$ GeV.\
           Note that the left panel is the\
           photon flux of the diffuse component reconstructed by the D$^3$PO\
           algorithm \citep{Selig2015} that analyzes\
           the photon data from the \textit{Fermi} Large Area Telescope \citep{Atwood2009}\
           and removes the contribution from point-like component.
           The red arrow at the center of the right\
           panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
           to the disc normal in 1.2 Myr.
  }
  \label{fig__gammaRay-map}
\end{figure*}

One can see that the general morphological characteristics of the \textit{Fermi} bubbles can be reproduced.\

% assuming a uniform CR spectrum with energy cutoff of ~500 GeV\
% and spectral index of 2.4, one could also reproduce the gamma-ray spectrum quite well.\
% Note that the simulation time at this point is 12.39 Myr,\
% much longer than the CR electron cooling time, so their Emax should\
% have cooled to below 500 GeV by this time (we should think about how to estimate this).\
% Therefore, the CRe generating the gamma-ray emission would need to be re-accelerated\
% by some in-situ acceleration mechanisms such as shocks or turbulence.\
% The forward shock is pretty far away from the gamma-ray bubbles,\
% so it's more likely associated with turbulence.

  Having successfully reproduced the morphology\
  and spectrum of the \textit{Fermi} bubbles,\
  we now ask whether CRe could also explain\
  the Galactic microwave haze.

  The microwave haze at 23 GHz was first detected by the \textit{WMAP} \citep{Dobler_2008}\
  within the region $|b|<30^{\circ}$ above and below the Galactic plane,\
  and later confirmed by the Planck Collaboration IX \citep{PlanckCollaborationIX2013}.

  The synchrotron emissivity with an isotropic electron pitch angle distribution\
  is given by \citet{BLUMENTHAL1970}:

  \begin{subequations}
     \begin{align}
        &\frac{dE}{dtd\nu dV} =\nonumber\\
        &\frac{4\pi\mathbb{C}e^{3}B^{0.5(p+1)}}{m_{\text{e}}c^{2}}\
        \left(\frac{3e}{4\pi m_{\text{e}}c}\right)^{0.5(p-1)}\
        a(p)\nu^{-0.5(p-1)},\\
        &a(p)=\nonumber\\
             &\frac{2^{0.5(p-1)}\sqrt{3}\Gamma\left[\left(3p-1\right)/12\right]\
                                        \Gamma\left[\left(3p+9\right)/12\right]\
                                        \Gamma\left[\left(p+5\right)/4\right]}
        {8\sqrt{\pi}(p+1)\Gamma\left[\left(p+7\right)/4\right]},
     \end{align}
     \label{synchrotron-emissivity}
  \end{subequations}

  where $\Gamma$ is gamma function, $B$ is the magnetic field strength defined in\
  \Cref{magnetic-field}.

  \Cref{fig__gammaRaySynchtronSpectrum} shows the simulated microwave (left)\
  and gamma-ray (right) spectra averaged over the different patches (shown in the legends) of the sky.

  For a given longitude and latitude range, the simulated spectra are\
  computed by projecting the gamma-ray/microwave emissivities as a\
  function of energy along finely sampled lines of sight\
  (with resolutions of 0.5 degrees), and then we average the spectra\
  over all the sight lines within the region.

  Indeed, we find that the simulated gamma-ray\
  spectra for all latitudes exhibit a spectral cutoff at\
  similar energies 400---500 GeV, consistent with\
  the observed cutoff energy.

  %The enhanced emission at the lower latitude would likely be due to
  %similar to the bottom right panel in Fig. 5 of YR17, which is dominated by\
  %the optical starlight. That's also why in your plot above,\
  %the high-latitude spectrum tends to be dimmer because of the decay of the ISRF intensity in optical.

\begin{figure*}
  \includegraphics[width=\linewidth]{figures/fig__spectrum.png}
  \caption{
      Simulated microwave spectra (colored lines in left) averaged over $20^{\circ}<|b|<30^{\circ}$, $|l|<10^{\circ}$.\
      The data point represents the \textit{WMAP} data in the 23 GHz K band and\
      the shaded bow-tie area indicates the range\
      of synchrotron spectral indices allowed for the \textit{WMAP} haze \citep{Dobler_2008}.\
      Simulated gamma-ray spectra (colored lines in right column)\
      of the \textit{Fermi} bubbles calculated for a longitude range of\
      $|l|<10^{\circ}$ for different latitude bins.\
      The gray band represents the observational data of \citet{Ackermann2014}.\
      The rows from top to bottom show the microwave (left) and gamma-ray (right) spectra\
      with CRe spectra index $2.2, 2.4$ and $2.6$.\
      The CRe cutoff energy is $1.1\times10^{6}m_{\text{e}}c^{2}$ in all cases.
      %At larger $p$, the microwave spectrum was found to be steeper as $I_{\nu}\propto \nu^{-(p-1)/2}$.
  }
  \label{fig__gammaRaySynchtronSpectrum}
\end{figure*}

The correlation between the multi-wavelength simulation suggest that\
the \textit{Fermi} bubbles are produced by high-energy electrons\
via an inverse Compton scattering process, as the same electrons can\
also simultaneously produce synchrotron radiations in the\
presence of magnetic fields.

@@

Since the jets encounter a larger column depth of clouds along their path,\
they interact more strongly with the dense ISM.\
The jets do not immediately clear a channel along the inclined axis of launch.\
Rather, the dense clouds deflect the jets, which then decelerate\
and launch a sub-relativistic outflow along the minor axis following the path of least resistance.

Assuming that a relativistic electron population of spectral
index x = 2.2 gives rise to the microwave haze via synchrotron
emission.
